Modern Graph Generators: A Survey

### 2018-09-16 challenges.tex
Updated privacy-preserving part

>>>>

\subsection{Privacy-preserving Graph Generation}

A lot of work has been conducted on techniques for publishing social network
graphs with privacy guarantees~\cite{wu2010survey}. However, the topic of
generating social graphs with a realistic structure yet private has been barely explored.

Most of the existing work falls within the topic of graph generation with ``differential
privacy''~\cite{dwork2009differential} guarantees. More specifically, in
~\cite{wang2013preserving} the authors develop a differential privacy graph
generation approach based on the dK-graph generation
model~\cite{mahadevan2006systematic} that outperforms the Stochastic Kronecker
Graph Model~\cite{LeskovecCKF05} in terms of the produced structural properties,
eventhough the results show that there is still room for improvement.

Following this line of research, recent work~\cite{qin2017generating} extends the notion of differential privacy
and propose an `` edge local differential privacy'' based graph generation
method. The poposed method allows generating privacy preserving synthetic social
graphs wihtout the need of a centralized data curator, while preserving structural
properties more accurately than straw-hat methods such as Randomized
Neighbor Lists (based on randomized response~\cite{dwork2014algorithmic}) and
Degree-based Graph Generation (which perturbates the original graph degrees
using the Laplace mechanism~\cite{dwork2009differential}). Again, eventhough the
proposed technique outperforms the baselines, the results show that there is
still room for improvement in terms of the structural properties of the
generated graph.
